\documentclass[line,margin]{res} 

\begin{document}

\name{Robert Bigaignon}
\address{1335 Clay street, San Francisco, 94109, CA}
\phone{+1 (551) 208-4129}
\email{robert.bigaignon@gmail.com}

\begin{resume}

\section{EXPERIENCE}
                {\sl Software Engineer --- Yelp (San Francisco, CA)} \hfill since 2011 \\
                Currently working as a backend engineer maintaining and developing Yelp's revenue system. My contributions to date include:
                \begin{itemize}  \itemsep -2pt
                    \item Implementation of a Direct Debit Tornado/Thrift service responsible for processing payments for UK accounts.
                    \item Implementation of a set of batches processing and consolidating advertising revenue into reports used by the finance department to report earnings.
                    \item Successfully mentored 3 engineers including two full-time new graduates and one intern.
                \end{itemize}

                {\sl Software Engineer --- Syncsort (Woodcliff Lake, NJ)} \hfill 2008-2011 \\
                Contributed to the development of DMExpress, a high performance ETL framework.
                \begin{itemize}  \itemsep -2pt
                    \item Design and implementation of DMExpress API allowing partners to accelerate their applications using DMExpress \texttt{C++} library.
                    \item Complete refactor of DMExpress' serialization module using Boost libraries.
                    \item Led an initiative to modernize Syncsort's infrastructure, which involved: migrating of in-house issue tracking system to Trac; promotion of Git as a replacement for legacy SCM; facilitating peer code review process.
                \end{itemize}

                {\sl Software Engineer Intern --- Siemens (Princeton, NJ)} \hfill Winter/Spring 2007 \\
                Contributed to RadBuilder, an image processing framework used for the rapid prototyping of application. My main contribution involved facilitating the segmentation of tumors in 3D images.
                \begin{itemize}  \itemsep -2pt
                    \item Implementation of implicit surface interpolation algorithms used for human guided surface segmentation.
                    \item Implementation of contour approximation algorithms.
                    \item Implementation parametric curves widgets.
                \end{itemize}

\section{INDEPENDENT WORK}
                {\sl Maarifa} \hfill 2011 \\
                Served as \textit{pro-bono} developer for Maarifa, a non-profit organization building an education platform in Kenya.
                \begin{itemize}  \itemsep -2pt
                    \item Designed and implementation of a web service facilitating the management and distribution of content to the students. The service was prototyped using Django.
                    \item Provided technical guidance to the CEO for the future development of the service.
                \end{itemize}

\section{EDUCATION} 
                {\sl Master of Science,} Computer Science \hfill 2008 \\
                Stevens Institute of Technology, Hoboken, New Jersey \\
                GPA: 4.0 \\
                \vspace{1pt} \\
                {\sl Bachelor of Science,} Computer Science \hfill 2007 \\
                EPITA, Kremlin-Bic\^etre, France \\
                GPA: 3.8

\section{SKILLS}
                Proficient: Python, \texttt{C/C++}. \\
                Tools and applications: GNU, MySQL, SQLAlchemy, Tornado, Thrift,
                 Git, Emacs, \LaTeX. \\

\end{resume}
\end{document}







